A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-12 main.tex
[WIP] Add some more comments.

Terms include ordinary explicitly typed \(\lambda\)-terms, constants,
whose type is declared in signature $\Sigma$, and the following five forms
related to multi-stage programming:
$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
$\Lambda\alpha.M$ is a stage variable abstraction;
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
$\%_\alpha M$ is an operator for cross-stage persistence.
The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
and applications are left-associative
and two abstractions extends as far to the right as possible.
For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.

@@

% Contexts
Contexts are sequences of triples of a variable, its type, and its stage.
$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.

\AI{We should note that constants and type variables are not staged.}
\subsection{Reduction}

Next, we define full reduction for \LMD.
Before giving the definition of reduction, we define two substitutions.
Substitution $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
Substitution $M[\alpha \mapsto \epsilon]$ is defined below.

\begin{align*}
	% \newcommand{\SB}{}
	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:\tau[\alpha \mapsto \epsilon].M[\alpha \mapsto \epsilon]                                  \\
	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]\ \epsilon                                                                \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta M[\alpha \mapsto \epsilon]                               & (\text{if } \alpha \neq \beta) \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                         & (\text{if } \alpha = \beta)    \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta M[\alpha \mapsto \epsilon]                              & (\text{if } \alpha \neq \beta) \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        & (\text{if } \alpha = \beta)    \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M[\alpha \mapsto \epsilon]                            & (\text{if } \alpha \neq \beta) \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}M[\alpha \mapsto \epsilon]      & (\text{if } \alpha \neq \beta) \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         & (\text{if } \alpha = \beta)    \\
\end{align*}

>>>>

Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
whose type is declared in signature $\Sigma$, and the following five forms
related to multi-stage programming:
$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
$\Lambda\alpha.M$ is a stage variable abstraction;
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
$\%_\alpha M$ is an operator for cross-stage persistence.
The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
and applications are left-associative
and two abstractions extends as far to the right as possible.
For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.

@@

% Contexts
Contexts \AI{Why not call them ``type environments'' to avoid confusion with evaluation contexts?} are sequences of triples of a variable, its type, and its stage.
$\textrm{Domain}$ is a function from a content to a set of variables defined in the context.
\AI{I'd prefer \textit{dom}.}
The side condition of $x\not\in\textrm{Domain}(\G)$ prevent multiple appearances of the same variable and
$x\not\in\textrm{FV}(\tau)$ is needed in the proof of Substitution Lemmas.

\AI{We should note that constants and type variables are not staged.}
\paragraph{Remark:}  \AI{Comparison with Hanada--Igarashi.}

\subsection{Reduction}

Next, we define full reduction for \LMD.
Before giving the definition of reduction, we define two kinds of substitutions.
Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
$N$ for $x$ in $M$, and we omit its definition here.
Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
for stage variable $\alpha$ in $M$ is defined below.
\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}

\begin{align*}
	% \newcommand{\SB}{}
	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
\end{align*}
